---
title: "Model"
author: "Rui Zou, Zhihao Ai"
output: html_document
---

# Load training set
```{r}
train <- read.table("./train.txt", header = F, sep = "\t")
colnames(train) <- c('age', 'gender_MALE', 'signup_method_facebook', 'signup_method_google', 'language_cs', 'language_da', 'language_de', 'language_el', 'language_en', 'language_es', 'language_fi', 'language_fr', 'language_hu', 'language_is', 'language_it', 'language_ja', 'language_ko', 'language_nl', 'language_no', 'language_pl', 'language_pt', 'language_ru', 'language_sv', 'language_th', 'language_tr', 'language_zh', 'signup_app_Moweb', 'signup_app_Web', 'signup_app_iOS', 'Y')
```

# Model with all variables
```{r}
lgr.full <- glm(Y~., data = train, family = binomial('logit'))
summary(lgr.full)
```

# Reduced model (based on summary of the model with all variables)
```{r}
lgr.reduced <- glm(Y~age+gender_MALE+signup_app_Moweb+signup_app_Web+signup_app_iOS, data = train, family = binomial('logit'))
summary(lgr.reduced)
```

# Load testing set
```{r}
test <- read.table("./test.txt", header = F, sep = "\t")
colnames(test) <- c('age', 'gender_MALE', 'signup_method_facebook', 'signup_method_google', 'language_cs', 'language_da', 'language_de', 'language_el', 'language_en', 'language_es', 'language_fi', 'language_fr', 'language_hu', 'language_is', 'language_it', 'language_ja', 'language_ko', 'language_nl', 'language_no', 'language_pl', 'language_pt', 'language_ru', 'language_sv', 'language_th', 'language_tr', 'language_zh', 'signup_app_Moweb', 'signup_app_Web', 'signup_app_iOS', 'Y')
```

# Forward selection
```
fit0 <- glm(Y ~ 1, data = train, family = binomial(link = "logit"))
fit.forward <- step(fit0, scope=list(lower=~1, upper=~age+gender_MALE+signup_method_facebook+signup_method_google+language_cs+language_da+language_de+language_el+language_en+language_es+language_fi+language_fr+language_hu+language_is+language_it+language_ja+language_ko+language_nl+language_no+language_pl+language_pt+language_ru+language_sv+language_th+language_tr+language_zh+signup_app_Moweb+signup_app_Web+signup_app_iOS), direction="forward", family = binomial(link = "logit"))
```
Results for forward selection:

Start:  AIC=44634.26, Y ~ 1

End: AIC=44504.2, Y ~ signup_app_Web + age + signup_app_Moweb + language_zh + language_it + language_fr + gender_MALE + language_cs + language_is
<!--
Results for forward selection:
Start:  AIC=44634.26
Y ~ 1
...
...
Step:  AIC=44504.2
Y ~ signup_app_Web + age + signup_app_Moweb + language_zh + language_it + language_fr + gender_MALE + language_cs + language_is
-->

# Backward selection
```
fitf <- glm(Y ~ ., data = train, family = binomial(link = "logit"))
fit.backward<-step(fitf, scope=list(lower=~1,
upper=~age+gender_MALE+signup_method_facebook+signup_method_google+language_cs+language_da+language_de+language_el+language_en+language_es+language_fi+language_fr+language_hu+language_is+language_it+language_ja+language_ko+language_nl+language_no+language_pl+language_pt+language_ru+language_sv+language_th+language_tr+language_zh+signup_app_Moweb+signup_app_Web+signup_app_iOS), direction="backward")
```
Results for backward selection:

Start:  AIC=44533.37
Y ~ age + gender_MALE + signup_method_facebook + signup_method_google + 
    language_cs + language_da + language_de + language_el + language_en + 
    language_es + language_fi + language_fr + language_hu + language_is + 
    language_it + language_ja + language_ko + language_nl + language_no + 
    language_pl + language_pt + language_ru + language_sv + language_th + 
    language_tr + language_zh + signup_app_Moweb + signup_app_Web + 
    signup_app_iOS
    
End:  AIC=44508.18
Y ~ age + gender_MALE + language_cs + language_el + language_en + 
    language_fr + language_is + language_it + signup_app_Moweb + 
    signup_app_Web

# Both (start from full model)
```
fit.both<-step(fitf, scope=list(lower=~1,
upper=~age+gender_MALE+signup_method_facebook+signup_method_google+language_cs+language_da+language_de+language_el+language_en+language_es+language_fi+language_fr+language_hu+language_is+language_it+language_ja+language_ko+language_nl+language_no+language_pl+language_pt+language_ru+language_sv+language_th+language_tr+language_zh+signup_app_Moweb+signup_app_Web+signup_app_iOS), direction="both")
```
Results for both (start from full model):

Start:  AIC=44533.37
Y ~ age + gender_MALE + signup_method_facebook + signup_method_google + 
    language_cs + language_da + language_de + language_el + language_en + 
    language_es + language_fi + language_fr + language_hu + language_is + 
    language_it + language_ja + language_ko + language_nl + language_no + 
    language_pl + language_pt + language_ru + language_sv + language_th + 
    language_tr + language_zh + signup_app_Moweb + signup_app_Web + 
    signup_app_iOS

End:  AIC=44504.2
Y ~ age + gender_MALE + language_cs + language_fr + language_is + 
    language_it + signup_app_Moweb + signup_app_Web + language_zh

# Both (start from model containing only intercept)
```
fit.both2<-step(fit0, scope=list(lower=~1,
upper=~age+gender_MALE+signup_method_facebook+signup_method_google+language_cs+language_da+language_de+language_el+language_en+language_es+language_fi+language_fr+language_hu+language_is+language_it+language_ja+language_ko+language_nl+language_no+language_pl+language_pt+language_ru+language_sv+language_th+language_tr+language_zh+signup_app_Moweb+signup_app_Web+signup_app_iOS),direction="both")
```
Results for both (start from model containing only intercept):

Start:  AIC=44634.26
Y ~ 1

End:  AIC=44504.2
Y ~ signup_app_Web + age + signup_app_Moweb + language_zh + language_it + 
    language_fr + gender_MALE + language_cs + language_is

# Likelihood Ratio Test for language predictors and signup_method predictors
Using `lrtest` from package `lmtest`
```{r, message = FALSE} 
library(lmtest)
```
```{r}
lrtest(lgr.reduced, lgr.full)
```
At $\alpha = 0.05$ level, since $G^2 = 31.429 \le \chi^2(1-\alpha;p - q) = \chi^2(1-0.05;29 - 6) = 35.17246$, we conclude $H_0$, that the coefficients of language predictors and signup_method predictors all equal zero and can be dropped from the full model.

# Likelihood Ratio Test for signup_app predictors
```{r}
lgr.reduced.wo.signup_app <- glm(Y~age+gender_MALE, data = train, family = binomial('logit'))
lrtest(lgr.reduced.wo.signup_app, lgr.reduced)
```
At $\alpha = 0.05$ level, since $G^2 = 85.196 > \chi^2(1-\alpha;p - q) = \chi^2(1-0.05;6 - 3) = 7.814728$, we reject $H_0$, that the coefficients of signup_app predictors can be dropped from the model. The signup_app predictors are retained.

# Wald Test for age predictor
```{r}
summary(lgr.reduced)
```
## age
At $\alpha = 0.05$ level, since $|z^*| = 5.155 > z(1-\alpha/2) = 2.326348$, we reject $H_0$, that the coefficient of age predictor can be dropped. The $p$-value of the test is $2.54e-07$.

## gender
At $\alpha = 0.1$ level, since $|z^*| = 2.072 > z(1-\alpha/2) = 2.053749$, we reject $H_0$, that the coefficient of gender predictor can be dropped. The $p$-value of the test is $0.038245$.

# Interpretation
```{r}
exp(coef(lgr.reduced))
```